Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-14 analyses/reproduce_analyses.Rmd
move eggegg_RF_Pref to come after the eggegg_model

RF_Pref <- bootstrap_fitness(
  logistic_model = foodweb_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)

# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots) 
```

@@

```{r Egg-Parasitoid-Selection}
eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
  select(-sc.Diam, -sc.log.Clutch) %>%
  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
  spread(Foodweb, absolute_fitness) %>%
  mutate(fitness_difference = Complex-Simple)

>>>>

RF_Pref <- bootstrap_fitness(
  logistic_model = foodweb_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)
```

@@

```{r Egg-Parasitoid-Selection}
# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)

eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
  select(-sc.Diam, -sc.log.Clutch) %>%
  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
  spread(Foodweb, absolute_fitness) %>%
  mutate(fitness_difference = Complex-Simple)
